Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-11-17 Paper/paper.tex
text to bank effectualness section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How are detection searches affected by not including NS matter effects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
See what is the loss in SNR if we recover NSBH signals with a template bank of
BH-BH waveforms? It is very likely that the answer would be: $<1\%$. But it
is very interesting to show that for spinning BHs!

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How are detection searches affected by not including NS matter effects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Near future detection searches with aLIGO are poised to search for NSBH
signals using BHBH templates. In this section, we examine the effect of ignoring
the effects of tidal deformation and disruption of the NS during inspiral and 
merger phases of search templates. We construct a template bank $\mathcal{B}$ 
restricted to the NSBH parameter space with $\mbh\in[2.5M_\odot, 20.5M_\odot]$, 
$\chibh\in[-0.5, +0.75]$, $\mns\in[1M_\odot,3M_\odot]$ and $\chi_\mathrm{NS}=0$,
using a PN-based geometric lattice placement method~\cite{Harry:2013tca}.

Before investigating its SNR recovery against tidal NSBH signals, we test the 
effectualness of this bank to point-particle NSBH signals,
in order to make sure that the placement method does not leave any region of
the binary parameter-space under-covered. We simulate $50,000$ signals with 
component-mass and BH spin values
sampled uniformly over their allowed ranges, and filter each of them against
the entire bank. For both signals and templates, we use the frequency-domain 
reduced-order model (ROM) of the SEOBNRv2 approximant~\cite{Purrer:2014} 
implemented within the LIGO algorithms Library~\cite{lal}. We record the 
fitting-factors~\cite{FittingFactorApostolatos} recovered by the bank for all
signals, which measures the fraction of optimal SNR that the bank is able
to recover. Fig.~\ref{} shows these FFs as a function of the injected
BH mass and BH spin, and Fig.~\ref{} provides a histogram of the recovered FF 
values. From these figures, we conclude that our bank is effectual as intended.

Next, tn order to establish the effect of NS matter effects on the SNR recovery of 
detection searches, we perform a similar calculation as above, with the
difference that the signals are now modelled using the model of tidal 
corrections to IMR amplitude and phasing published in 
Ref.~\cite{Lackey:2013axa}, applied to SEOBNRv2 as the underlying BHBH model.
